Adaptive group-regularized logistic elastic net regression

### 2019-04-01 docs/manuscript.Rnw

	Recently, \cite{zhang_novel_2018} introduced VBVS, a method similar to ours in
	spirit. Nevertheless, one clear advantage of our method over VBVS is the
	possibility of adaptive inclusion of external information on the features to
	aid in prediction and feature selection. Bayesian versions of support vector 
	machines have been used in classification problems as well 
	\cite[]{chakraborty_bayesian_2011}, but these methods also lack 
	adaptive inclusion of external information on the features.

	In line with the above, our proposed method is (a) subjective: the 
	hyper-parameters are estimated from the data and not chosen on objective 
	grounds, (b) adaptive: prior information is automatically and subjectively 
	weighed with respect to its informativeness, (c) fast compared to full 
	Bayesian analysis or cross-validation, and (d) requires minimal input by the 
	user: only the data and grouping of the features is required. We emphasize that 
	our method is different from recent developments in grouped penalized 
	regression such as \cite{dondelinger_joint_nodate}, where instead of the 
	features, the observations are partitioned.

>>>>

	Recently, \cite{zhang_novel_2019} introduced VBVS, a method similar to ours in
	spirit. Nevertheless, one clear advantage of our method over VBVS is the
	possibility of adaptive inclusion of external information on the features to
	aid in prediction and feature selection. Bayesian versions of support vector 
	machines have been used in classification problems as well 
	\cite[]{chakraborty_bayesian_2011}, but these methods also lack 
	adaptive inclusion of external information on the features.

	In line with the above, our proposed method is (a) subjective: the 
	hyper-parameters are estimated from the data and not chosen on objective 
	grounds, (b) adaptive: prior information is automatically and subjectively 
	weighed with respect to its informativeness, (c) fast compared to full 
	Bayesian analysis or cross-validation, and (d) requires minimal input by the 
	user: only the data and grouping of the features is required. We emphasize that 
	our method is different from recent developments in grouped penalized 
	regression such as \cite{dondelinger_joint_2018}, where instead of the 
	features, the observations are partitioned.
